Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-09 main.tex
storyline of intro, joint with SK

    %%% CONTEXT %%%
    Only mapping tasks to processors is not enough.
    Reusing processors is important to achieve good makespans.

    %%% MOTIVATION %%%
    HEFT is one of the most popular heuristics (cite a review).
    However, existing HEFT variations do not take memory sizes into consideration (\skug{check in related work if true!}).

    %%% CONTRIBUTION %%%
    In this paper, we formulate the problem that takes memories into consideration.
    We propose three HEFT-based heuristics that take memory size into account: \heftbl, \heftblc, and \heftmm.
    The difference is the way they order tasks for scheduling.
    We compare our heuristics to a baseline HEFT variant that does not take memory sizes into account.

    We find that our heuristics are able to schedule all workflows correctly, and produce makespans similar to the baseline.

>>>>

    %%% CONTEXT %%%
    \begin{itemize}
      \item What is a scientific workflow?
      \item Scientific workflows are all over the place $\rightarrow$ important!
      \item Scheduling (order, maybe even concrete starting times) is important for efficient workflow executions
      \item Only mapping tasks to processors is not enough.
      \item This also allows to reuse processors, which is important to achieve good HW utilization / makespans (explain!).
    \end{itemize}

    %%% MOTIVATION %%%
    \begin{itemize}
      \item Heterogeneous means: different CPU speeds, different mem sizes
      \item With different mem sizes: more difficult to adhere to mem constraints
      \item Adhering to memory constraints is very important to avoid execution failures.
      \item In this paper, we formulate the problem that takes memories into consideration (using (nearly the) model from ICPP paper)
      \item HEFT (see book chapter) is one of the most popular heuristics (cite a review).
      \item However, existing HEFT variations do not take memory sizes into consideration (\skug{check in related work if true!}).
        Note: 2 papers that deal with memory sizes, but model is very different!
      \item Many scheduling strategies assume that task running times provided to them are accurate. This is not really the case
        in practice. Thus, one needs to adapt the schedule when major deviations occur (which is the case in practice).
        List-based schedulers such as HEFT are not designed for adaptation and would compute a completely schedule from scratch.
    \end{itemize}

    %%% CONTRIBUTION %%%
    \paragraph*{Contribution}
    \begin{itemize}
      \item We propose three HEFT-based heuristics that take memory sizes into account: \heftbl, \heftblc, and \heftmm.
      \item The difference between the new heuristics is the way they rank tasks (for processor assignment).
      \item Static: we compare our heuristics to a baseline HEFT variant that does not take memory sizes into account.
      \item Static: we find that our heuristics are able to schedule all workflows correctly, and produce makespans similar to the baseline.
      \item Adaptive: runtime system built, simulates workflow executions and deviations in running times and mem requirements of tasks
      \item Answering requests of the runtime system for adaptation, the scheduler computes an improved schedule based on the reported deviations.
    \end{itemize}
